### 2021-04-19 README.rmd
minor edit in readme
preparing for a submission to JOSS

@@

Provides functions to apply Spatial Fuzzy c-means 
Algorithm, visualize and interpret results. This method is 
well suited when the user wants to analyze data with a 
fuzzy clustering algorithm and to account for the spatial dimension of 
the dataset. Tests for estimating the spatial consistency and classification 
quality are proposed in addition. The algorithms were developped first for 
brain imagery as described in the articles of [Cai and al. 2007](https://doi.org/10.1016/j.patcog.2006.07.011) and [Zaho and al. 2013](https://doi.org/10.1016/j.dsp.2012.09.016). [Gelb and Apparicio](https://doi.org/10.4000/cybergeo.36414) proposed to apply the method to perform a socio-residential and environmental taxonomy in Lyon (France).

>>>>

## Contributors

@@

Provides functions to apply Spatial Fuzzy c-means 
Algorithm, visualize and interpret results. This method is 
well suited when the user wants to analyze data with a 
fuzzy clustering algorithm and to account for the spatial dimension of 
the dataset. Indexes for measuring the spatial consistency and classification 
quality are proposed in addition. The algorithms were developed first for 
brain imagery as described in the articles of [Cai and al. 2007](https://doi.org/10.1016/j.patcog.2006.07.011) and [Zaho and al. 2013](https://doi.org/10.1016/j.dsp.2012.09.016). [Gelb and Apparicio](https://doi.org/10.4000/cybergeo.36414) proposed to apply the method to perform a socio-residential and environmental taxonomy in Lyon (France).
